Finch: Sparse and Structured Array Programming with Control Flow

### 2024-04-25 sections/appendix.tex
fix

\textbf{Fig1008\_a\_\_step edge\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/Fig1008\_a\_\_step edge\_.png}}

@@

\textbf{Fig0503 \_original\_pattern\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/Fig0503 \_original\_pattern\_.png}}

>>>>

\textbf{Fig1008\_a\_\_step\_edge\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/Fig1008\_a\_\_step\_edge\_.png}}

@@

\textbf{Fig0503\_\_original\_pattern\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/Fig0503\_\_original\_pattern\_.png}}
